---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

```{r, include=TRUE}
library(classdata)
 data(ames)
 
 summary(ames)
 
 head(ames)
 
 unique(ames$`Multi Sale`)
```
<<<<<<< HEAD
## Step 1.
 1. What variables: Parcel ID, Address, Style, Occupancy, Sale Date, Sale Price, Multi Sale, YearBuilt, Acres, TotalLivingArea (sf), Bedrooms, FinshedBsmtArea (sf), LotArea(sf), AC, FirePlace, Neighborhood. The variables are of type character, numerical, and date.
 
=======
 1. What variables: Parcel ID, Address, Style, Occupancy, Sale Date, Sale Price, Multi Sale, YearBuilt, Acres, TotalLivingArea (sf), Bedrooms, FinshedBsmtArea (sf), LotArea(sf), AC, FirePlace, Neighborhood. The variables are of type character, numerical, and date. What do these variables mean: Sale date is the date of the sale of the property, expected data range 2017-2022. Sale price is the amount of money in American dollars that the property was sold for, expected range 0, 20 million. Multi Sale shows if the sale consisted of more than one property, Y showing that it was, NA otherwise, expected possible values, NA and Y. YearBuilt is the year that the house or building was built, expected range, 0-2022.
Parcel ID: A unique ID used to identify a property to authorities, this could be any range of unique values.
Address: This represents the address of the property. This is expected to not be empty, but it could be any address.
Style: This marks the style of the house / property, the range for this dataset is: 1 Story Frame, 2 Story Frame, 1 1/2 Story Frame, Split Level Frame, Split Foyer Frame, (Other), or NA.
Occupancy: This marks what type of occupancy it is, the ranges we expect for this dataset are: Condominium, Single-Family / Owner Occupied, Townhouse, Two-Family Conversion, Two-Family Duplex, or NA.
Acres: Represents the size of the lot on which the residence is located. Values range from 0 to 12.
TotalLivingArea: Indicates the total interior living space of the residence. Values range from 0 to 6,000 square feet.
Bedrooms: The number of bedrooms in the residence. This ranges from 0 to 10, with some missing values.
FinishedBasementArea: Refers to the finished area of the basement in square feet. Values range from 10 to 6,494 square feet, with some missing values.
LotArea(sf): It is a Square feet area of a house for a particular house sale home.it is measured by Square feet and the range will be from 1000 sf. 
AC: It says whether a house has AC or not. There will be no range because it is yes or no thing.
Fireplace: It will say that whether they has a fireplace or not in a house. I think their will no range because it is yes or no thing.
Neibhorhood: It says in which area is it located. Their will not range for that too.
 

## Step 2.
The main variable for this report is `Sale Price`, we will be focusing on exploring relations between it and other variables in the dataset.

## Step 3

Range of Sales Price:

```{r}
min(ames$`Sale Price`)
max(ames$`Sale Price`)


range(ames$`Sale Price`)


diff(range(ames$`Sale Price`))
```

The range of home sale prices in the Ames dataset spans from the 0 sale price to the 20500000, showing the spread of values across the housing market.
 
```{r}
library(tidyverse)

ggplot(ames, aes(x = `Sale Price`)) +
  geom_bar(fill = "steelblue", color = "Black") +
  labs(
    title = "Distribution of Sale Prices",
    x = "Sale Price",
    y = "Count"
  )
```
 
 
 The histogram of Sale Price shows a right-skewed distribution where most homes sell at lower to mid-range prices, but a few extremely high-priced outliers in the millions stretch the scale and make the main pattern harder to see.
 
 
## Step 4
 
 Norah's work: 
 One variable that could be related to the main variable, Sale Price, is Year Built. The range of this variable is 0-2022. 
```{r}

ggplot(ames, aes(y = `Sale Price`, x = `YearBuilt`)) +
  geom_point(fill = "steelblue", color = "Black") +
  labs(
    title = "Distribution of Sale Prices",
    x = "Sale Price",
    y = "Year Built"
  )
#This is clearly too compressed, we will remove the year values of 0.
# and also sale prices over 1 million since there are only a few and we need to see the overall pattern.
ames %>%
  filter(YearBuilt != 0, `Sale Price` <=1000000) %>%
  ggplot(aes(y = `Sale Price`, x = YearBuilt)) +
  geom_point(color = "Black", fill = "steelblue", size = 2, alpha = 0.5) +
  labs(
    title = "Distribution of Sale Prices vs. Year Built (excluding YearBuilt = 0)",
    x = "Year Built",
    y = "Sale Price"
  ) +
  theme_minimal()
#This plot shows a general positive correlation between year built and sale price.
```
