---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

```{r, include=TRUE}
library(classdata)

 summary(ames)
 
 head(ames)
 
 unique(ames$`Multi Sale`)
```
 1. What variables: Parcel ID, Address, Style, Occupancy, Sale Date, Sale Price, Multi Sale, YearBuilt, Acres, TotalLivingArea (sf), Bedrooms, FinshedBsmtArea (sf), LotArea(sf), AC, FirePlace, Neighborhood. The variables are of type character, numerical, and date. What do these variables mean: Sale date is the date of the sale of the property, expected data range 2017-2022. Sale price is the amount of money in American dollars that the property was sold for, expected range 0, 20 million. Multi Sale shows if the sale consisted of more than one property, Y showing that it was, NA otherwise, expected possible values, NA and Y. YearBuilt is the year that the house or building was built, expected range, 0-2022.
 
 
 
 
